### 2010-06-30 trunk/paper/IIWAS2010/content/system_arch.tex
merged changes

Once we have relevant QRMs through QRM ranking for a given user query, we can get answers by re-running the pathways with help of the \emph{Query Resolution Engine} (QRE) of Morpheus. The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, and highlighting of datato form a text answer.

>>>>

Once we have relevant QRMs through QRM ranking for a given user query, we can produce answers by re-running the pathways.

 The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, and highlighting of data to form a text answer.  The QRE assumes that becuase of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.  It uses the relative XPath location to the answer node on HTML pages as described in \cite{Badica06}.
